Appendix

### 2020-05-01 appendix/appendixV5.Rmd
Table 3 Permutation.

## Summary of Models

@@

\blandscape
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = T,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "T",
        "P-Value",
        #
        "Estimate",
        "SE",
        "T",
        "P-Value",
        #
        "Estimate",
        "SE",
        "T",
        "P-Value"
      )
    ) %>% 
  collapse_rows(
    1:3,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 4, "logExpPC" = 4, "PCTGDP" = 4)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header"))

>>>>

@@

\blandscape
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = T,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "T",
        "P-Value",
        #
        "Estimate",
        "SE",
        "T",
        "P-Value",
        #
        "Estimate",
        "SE",
        "T",
        "P-Value"
      ),
  caption = "Summary of Models"
    ) %>% 
  collapse_rows(
    1:3,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 4, "logExpPC" = 4, "PCTGDP" = 4)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header"))

```{r, echo=F, warning=F,error=F,message=F}
coefs = bind_rows(
  mod1_permu,
  mod2_permu,
  mod3_permu,
  mod4_permu,
  mod5_permu) %>%
  select(` `) %>%
  distinct()

aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(type = "Base") %>%
  select(type, everything())

aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order)
         ) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(type = "All Coefs") %>%
  select(type, everything())

\blandscape
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = T,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "T",
        "P-Value",
        #
        "Estimate",
        "SE",
        "T",
        "P-Value",
        #
        "Estimate",
        "SE",
        "T",
        "P-Value"
      ),
          caption = "Summary of Models (Permutest)"
    ) %>% 
  collapse_rows(
    1:3,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 4, "logExpPC" = 4, "PCTGDP" = 4)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header"))
